---
title: "Hard Work 3"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    code_folding: hide
---

## Instructions

1. Study Sections 3.1-3.8 of Chapter 3: "Diagnostics and Remedial Measures."    
<span id=note>(We will study more of Chapter 3 next week.)</span>


2. Attempt and submit at least <span id=points style="padding-left:0px;">{52}</span> Hard Work Points by Saturday at 11:59 PM.    
<span id=note>Over <span id=points style="padding-left:0px;">{56}</span> gets you {+1} Final Exam Point.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{62}</span> gets you {+2} Final Exam Points.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{70}</span> gets you {+3} Final Exam Points.</span>

## Reading Points <span id=headpoints>{30} Possible</span>

<div style="padding-left:20px;">

### Section 3.1 <span id=recpoints>{2}</span><span id=report>{ 2/2}</span>

### Section 3.2 <span id=recpoints>{2}</span><span id=report>{ 1.5/2 }</span>

### Section 3.3 <span id=recpoints>{8}</span><span id=report>{ 7/8}</span>

### Section 3.4 <span id=recpoints>{2}</span><span id=report>{ / }</span>

### Section 3.5 <span id=recpoints>{2}</span><span id=report>{ / }</span>

### Section 3.6 <span id=recpoints>{6}</span><span id=report>{ / }</span>

### Section 3.7 <span id=recpoints>{7}</span><span id=report>{ / }</span>

### Section 3.8 <span id=recpoints>{1}</span><span id=report>{ / }</span>

</div>

## Theory Points <span id=headpoints>{9} Possible</span>

<div style="padding-left:20px;">

### 3.1 <span id=recpoints>{2}</span><span id=report>{ 1/2 }</span>

The residual is the distance between $Y_i$ and $Yhat_i$.which is represented by $e_i = Y_i - Yhat_i$

The studentized residual is the 

$$
e*_i = (e_i - ebar) \div (sqrt(MSE))
$$

$\sigma$ = sqrt(MES) = $\sum(Y_i - Yhat_i)/sqrt(n - 2)$

The purpose of the semistudentized residual is to simplify residuals. $e_i$ is complex because it's for each individual error term. $e*_i$ allows us to use one measurement for each all points. 


 
### 3.12 <span id=points>{2}</span><span id=report>{ / }</span>

### 3.21 <span id=points>{3}</span><span id=report>{ / }</span>

### 3.23 <span id=points>{2}</span><span id=report>{ / }</span>


</div>


## Application Points <span id=headpoints>{32} Possible</span>

<div style="padding-left:20px;">

<a id=datalink style="font-size:.9em;" target="_blank" href=http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/index.html>Data Files</a>

### 3.3 <span id=recpoints>{6}</span><span id=report>{ 3/6 }</span>

```{r p33}
# Load the Data:
p1.19 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR19.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.19) <- c("Y","X")

p1.19.lm <- lm(p1.19)

boxplot(p1.19.lm$residuals)

plot(p1.19.lm$residuals, pch = 16, cex = 0.8)

plot(p1.19.lm$residuals ~ p1.19$X)

plot(p1.19.lm, which  = 2:2)

```

a. It seems that there are some outliers due to the points laying almost 3 standard deviations away from the mean. 

b. This plot shows that there is an outlier in the point that is ranked around 8 or 9. 

c. It seems that there is constant variance in this structure. This shows that there is consant variance and the error terms are normally distributed

d. 


### 3.4 <span id=recpoints>{6}</span><span id=report>{ /6 }</span>

```{r p34}
# Load the Data:
p1.20 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")

p1.20.lm <- lm(p1.20)

stem(p1.20$X, scale = 1)

```


### 3.5 <span id=recpoints>{5}</span><span id=report>{ / }</span>

```{r p35}
# Load the Data:
p1.21 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR21.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.21) <- c("Y","X")
```


### 3.6 <span id=points>{5}</span><span id=report>{ / }</span>

```{r p36}
# Load the Data:
p1.22 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```


### 3.7 <span id=points>{4}</span><span id=report>{ / }</span>

```{r p37}
# Load the Data:
p1.27 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR27.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.27) <- c("Y","X")
```


### 3.8 <span id=points>{3}</span><span id=report>{ / }</span>

```{r p38}
# Load the Data:
p1.28 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR28.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.28) <- c("Y","X")
```


### 3.13 <span id=recpoints>{3}</span><span id=report>{ / }</span>

```{r p313}
# Load the Data:
p1.20 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")
```



</div>










 <style>
#points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#report {
  font-size:.7em;
  padding-left:15px;
  font-weight:normal; 
  color:#5a5a5a;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}
</style>


<footer>
</footer>



 

 

 

 