---
title: "Hard Work 2"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---


## Instructions

1. Study Sections 2.1-2.10 of Chapter 2: "Inferences in Regression and Correlation Analysis."    
<span id="note">(Pace yourself, you have two weeks to work on this assignment.)</span>

2. Attempt and submit at least <span id=points style="padding-left:0px;">{83}</span> Hard Work Points by Saturday at 11:59 PM.    
<span id=note>Over <span id=points style="padding-left:0px;">{92}</span> gets you {+1} Final Exam Point.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{100}</span> gets you {+2} Final Exam Points.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{107}</span> gets you {+3} Final Exam Points.</span>

<br/>

##Notes

There is always a hypotheses for each parameter in the model. $beta_0$ and $beta_1$ are usually equal to or not equal to zero.

$b_0$ - $beta_{00}$

This is the PT function

```{r echo=TRUE}
plot(speed~dist, data = cars)
cars.lm <- lm(speed ~ dist, data = cars)
summary(cars.lm)

#this is the way we calculate our p-value by hand
#Pr(>\t\) just means that the probablility is two-tailed 

2*pt(9.474, 48, lower.tail = FALSE)

#this is calculating the critical value. 0.25 is our alpha or level of significance
qt(1-0.25/2, 48)

#This is the confidence interval equation and margin of error
#  b0 +or- t(1-a/2; n-2)S{b0}

8.28391 + qt(1-0.05/2, 48)*0.87438
8.28391 - qt(1-0.05/2, 48)*0.87438

confint(cars.lm)

#Also confint(cars.lm, level = (confidence interval))
#this is how to calculate the residuals

sum(cars.lm$residuals^2)

sqrt(sum(cars.lm$residuals^2)/48)

#prediction interval
predict(cars.lm, data.frame(dist=50), interval = "prediction")

predict(cars.lm, data.frame(dist=50), interval = "confidence")


```

## Reading Points <span id=headpoints>{40} Possible</span>

### Section 2.1 <span id=recpoints>{6}</span><span id=report>{ 3/6 }</span>

### Section 2.2 <span id=recpoints>{3}</span><span id=report>{ 3/3 }</span>

### Section 2.3 <span id=recpoints>{1}</span><span id=report>{ 1/1 }</span>

### Section 2.4 <span id=recpoints>{4}</span><span id=report>{ 3/4}</span>

### Section 2.5 <span id=recpoints>{6}</span><span id=report>{ 5/ 6}</span>

### Section 2.6 <span id=recpoints>{3}</span><span id=report>{ 3/3}</span>

### Section 2.7 <span id=recpoints>{8}</span><span id=report>{ 5/ 8}</span>

### Section 2.8 <span id=recpoints>{4}</span><span id=report>{ 1/ 4}</span>

### Section 2.9 <span id=recpoints>{3}</span><span id=report>{ / }</span>

### Section 2.10 <span id=recpoints>{2}</span><span id=report>{ / }</span>


<br/>




## Theory Points <span id=headpoints>{33} Possible</span>

### Problem 2.1 <span id=points>{1}</span><span id=report>{ / }</span>
 
### Problem 2.2 <span id=points>{1}</span><span id=report>{ / }</span>
 
### Problem 2.3 <span id=points>{1}</span><span id=report>{ / }</span>

### Problem 2.9 <span id=points>{1}</span><span id=report>{ / }</span>
 
### Problem 2.11 <span id=points>{1}</span><span id=report>{ / }</span>
 
### Problem 2.12 <span id=points>{1}</span><span id=report>{ / }</span>

### Problem 2.18 <span id=points>{1}</span><span id=report>{ / }</span>
<span id=headnote>Hint: Read page 71</span>
 
### Problem 2.19 <span id=points>{1}</span><span id=report>{ / }</span>

### Problem 2.20 or 2.21 or 2.22 <span id=points>{1}</span><span id=report>{ / }</span>

### Problem 2.33 <span id=recpoints>{3}</span><span id=report>{ / }</span>

### Problem 2.50 <span id=points>{2}</span><span id=report>{ / }</span>

### Problem 2.51 <span id=points>{2}</span><span id=report>{ / }</span>

### Problem 2.53 <span id=points>{4}</span><span id=report>{ / }</span>

### Problem 2.66 <span id=recpoints>{5}</span><span id=report>{ / }</span> 

<span id=note>R-Code Hint: rnorm(5, 0, sqrt(25))</span>

### Exercise 2.55 <span id=recpoints>{2}</span><span id=report>{ / }</span>

### Exercise 2.57 <span id=points>{3}</span><span id=report>{ / }</span>

### Exercise 2.61 <span id=points>{3}</span><span id=report>{ / }</span>

 

<br/>



## Application Points <span id=headpoints>{53} Possible</span>

<a id=datalink target="_blank" href=http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/index.html>Data Files</a>


### Problem 2.1 <span id=points>{1}</span><span id=report>{ / }</span>

### Problem 2.4 <span id=recpoints>{4}</span><span id=report>{ / }</span>

```{r p4}
# Load the Data:
p1.19 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR19.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.19) <- c("Y","X")
```


### Problem 2.5 <span id=recpoints>{4}</span><span id=report>{ / }</span> 

```{r p5}
# Load the Data:
p1.20 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")
```


### Problem 2.7 <span id=points>{3}</span><span id=report>{ / }</span> 

```{r p7}
# Load the Data:
p1.22 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```


### Problem 2.10 <span id=recpoints>{2}</span><span id=report>{ / }</span> 


### Problem 2.13 <span id=recpoints>{4}</span><span id=report>{ / }</span> 

```{r p13}
# Load the Data:
p1.19 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR19.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.19) <- c("Y","X")
```


### Problem 2.14 <span id=points>{4}</span><span id=report>{ / }</span> 

```{r p14}
# Load the Data:
p1.20 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")
```


### Problem 2.15 <span id=points>{4}</span><span id=report>{ / }</span>

```{r p15}
# Load the Data:
p1.21 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR21.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.21) <- c("Y","X")
```


### Problem 2.16 <span id=recpoints>{5}</span><span id=report>{ / }</span> 

```{r p16}
# Load the Data:
p1.22 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```


### Problem 2.25 <span id=recpoints>{5}</span><span id=report>{ / }</span>

```{r p25}
# Load the Data:
p1.20 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")
```


### Problem 2.26 <span id=recpoints>{4}</span><span id=report>{ / }</span>

```{r p26}
# Load the Data:
p1.22 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```


### Problem 2.29 <span id=recpoints>{5}</span><span id=report>{ / }</span> 

```{r p29}
# Load the Data:
p1.27 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR27.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.27) <- c("Y","X")
```


### Problem 2.30 <span id=points>{5}</span><span id=report>{ / }</span> 

```{r p30}
# Load the Data:
p1.28 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR28.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.28) <- c("Y","X")
```

### Problem 2.32 <span id=points>{3}</span><span id=report>{ / }</span> 

```{r p32}
# Load the Data:
p1.28 <- read.table("https://netfiles.umn.edu/users/nacht001/www/nachtsheim/Kutner/Chapter%20%201%20Data%20Sets/CH01PR28.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.28) <- c("Y","X")
```



<br />



 

 
 
 
 <style>
#points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#report {
  font-size:.7em;
  padding-left:15px;
  font-weight:normal; 
  color:#5a5a5a;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}
</style>


 

 