---
title: "Hard Work 3"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    code_folding: hide
---

```{r message=FALSE, warning=FALSE}
library(car)
library(mosaic)
library(ggplot2)
library(lmtest)
library(alr3)
```

## Instructions

1. Study Sections 3.1-3.8 of Chapter 3: "Diagnostics and Remedial Measures."    
<span id=note>(We will study more of Chapter 3 next week.)</span>


2. Attempt and submit at least <span id=points style="padding-left:0px;">{52}</span> Hard Work Points by Saturday at 11:59 PM.    
<span id=note>Over <span id=points style="padding-left:0px;">{56}</span> gets you {+1} Final Exam Point.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{62}</span> gets you {+2} Final Exam Points.</span>    
<span id=note>Over <span id=points style="padding-left:0px;">{70}</span> gets you {+3} Final Exam Points.</span>

## Reading Points <span id=headpoints>{30} Possible</span>

<div style="padding-left:20px;">

### Section 3.1 <span id=recpoints>{2}</span><span id=report>{ 2/2}</span>

### Section 3.2 <span id=recpoints>{2}</span><span id=report>{ 1.5/2 }</span>

### Section 3.3 <span id=recpoints>{8}</span><span id=report>{ 7/8}</span>

### Section 3.4 <span id=recpoints>{2}</span><span id=report>{ 2/2 }</span>

### Section 3.5 <span id=recpoints>{2}</span><span id=report>{ 2/2 }</span>

### Section 3.6 <span id=recpoints>{6}</span><span id=report>{ 5/6 }</span>

### Section 3.7 <span id=recpoints>{7}</span><span id=report>{ 7/7 }</span>

### Section 3.8 <span id=recpoints>{1}</span><span id=report>{ 1/1 }</span>

</div>

## Theory Points <span id=headpoints>{9} Possible</span>

<div style="padding-left:20px;">

### 3.1 <span id=recpoints>{2}</span><span id=report>{ 2/2 }</span>

The residual is the distance between $Y_i$ and $Yhat_i$.which is represented by $e_i = Y_i - Yhat_i$

The studentized residual is the 

$$
e*_i = (e_i - ebar) \div (sqrt(MSE))
$$

$\sigma$ = sqrt(MES) = $\sum(Y_i - Yhat_i)/sqrt(n - 2)$

The purpose of the semistudentized residual is to simplify residuals. $e_i$ is complex because it's for each individual error term. $e*_i$ allows you to measure according to standard deviations instead of raw measurements. This helps give perspective. 


 
### 3.12 <span id=points>{2}</span><span id=report>{ / }</span>

### 3.21 <span id=points>{3}</span><span id=report>{ / }</span>

### 3.23 <span id=points>{2}</span><span id=report>{ / }</span>


</div>


## Application Points <span id=headpoints>{32} Possible</span>

<div style="padding-left:20px;">

<a id=datalink style="font-size:.9em;" target="_blank" href=http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/index.html>Data Files</a>

### 3.3 <span id=recpoints>{6}</span><span id=report>{ 6/6 }</span>

```{r p33, message=FALSE, warning=FALSE}
# Load the Data:
p1.19 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR19.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.19) <- c("Y","X")

p1.19.lm <- lm(p1.19)

boxplot(p1.19$X)

names(p1.19.lm)

plot(p1.19.lm$residuals, pch = 16, cex = 0.8)

plot(p1.19.lm$residuals ~ p1.19.lm$fitted.values)

plot(p1.19.lm, which  = 2:2)

qq.p1.19 <- qqnorm(p1.19.lm$residuals)

qqPlot(p1.19.lm$residuals)

names(qq.p1.19)

cor(qq.p1.19$x, qq.p1.19$y)

Group1 <- p1.19$X < 26
Group2 <- p1.19$X >= 26

med1 <- median(p1.19.lm$residuals[Group1])
med2 <- median(p1.19.lm$residuals[Group2])

d1 <- abs(p1.19.lm$residuals[Group1] - med1)
d2 <- abs(p1.19.lm$residuals[Group2] - med2)

s2BF <- ( sum((d1-mean(d1))^2) + sum((d2 - mean(d2))^2))/(120-2)
sBF <- sqrt(s2BF)
tBF <- (mean(d1) - mean(d2))/(sBF*sqrt(1/sum(Group1)+1/sum(Group2)))


qt(1-0.01/2, 120-2)

tBF

2*pt(-abs(tBF), 120-2)

p1.19extra <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%203%20Data%20Sets/CH03PR03.txt")

colnames(p1.19extra) <- c("Y","X","X2","X3")


plot(p1.19.lm$residuals ~ p1.19extra$X2, xlab = "IQ")
plot(p1.19.lm$residuals ~ p1.19extra$X3, xlab = "Class Rank")


```

a. It seems that there are some outliers due to the points laying almost 3 standard deviations away from the mean. 

b. This plot shows that there is an outlier in the point that is ranked around 8 or 9. 

c. This should show no recognizable order which means that the relation between X and Y is linear. We can also check or outliers. This we can see that there is one. The data looks linear. 

d. Our correlation coefficient for x and y is 0.9744 and the critical value is 0.98. We conclude that the data is not normal. 

e. Because the absolute value BF t statistic is less than our critical value, there is constant variance. 

f. It looks like the IQ data should be included in the plot because it has an obvious pattern that would be beneficial to the original plot.


### 3.4 <span id=recpoints>{6}</span><span id=report>{ 6/6 }</span>

```{r p34, message=FALSE, warning=FALSE}
# Load the Data:
p1.20 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

p1.20extra <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%203%20Data%20Sets/CH03PR04.txt")

colnames(p1.20extra) <- c("Y","X","X2","X3")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")

p1.20.lm <- lm(p1.20)

stripchart(p1.20$X, method = 'stack', pch = 16)

plot(p1.20.lm$residuals, type = 'b', pch = 16, cex = 0.8)

stem(p1.20.lm$residuals)

plot(p1.20.lm$residuals ~ p1.20.lm$fitted.values)

plot(p1.20.lm, where = 1)

plot(p1.20.lm$residuals ~ p1.20$X)

plot(p1.20.lm, where = 1:3)

qqPlot(p1.20.lm$residuals)

qq.p1.20 <- qqnorm(p1.20.lm$residuals)

names(qq.p1.20)

cor(qq.p1.20$x, qq.p1.20$y)

bptest(p1.20.lm)

plot(p1.20extra$X2 ~ p1.20.lm$residuals)

plot(p1.20extra$X3 ~ p1.20.lm$residuals)

```

a. This shows that there are multiple observations with single xi values. There are no outliers. 

b. This shows that the errors are independent. Time is not a factor. 

c. It looks like there may be some outliers. It may also be left-skewed. 

d. They do provide the same information. X and Y seem to be linear and there are no outliers. 
e. Critical Value = 0.977

Correlation Coefficient = 0.9889

We conclude that the data is normal. 

f. They don't look like they're correlated over time. There is no serious trend of increase or decrease. 

g. If X2* < X2, then we conclude $H_o$

because BP = 1.4187 and our p-value is 0.2336, we conclude the null. 

h. In plotting these, it seems the the mean operational age of copiers serviced on the call has a significant effect on the data. It should be included. 

### 3.5 <span id=recpoints>{5}</span><span id=report>{ 5/5 }</span>

```{r p35}
# Load the Data:
p1.21 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR21.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.21) <- c("Y","X")

p1.21.lm <- lm(p1.21)

stripchart(p1.21$X, method = 'stack', pch = 16)

plot(p1.21.lm$residuals, type = 'b', pch = 16, cex = 0.8)

stem(p1.21.lm$residuals)

plot(p1.21.lm$residuals ~ p1.21$X)

group1 <- p1.21$X > 1.5
group2 <- !group1

med1 <- median(p1.21.lm$residuals[group1])
med2 <- median(p1.21.lm$residuals[group2])

D1 <- abs(p1.21.lm$residuals[group1] - med1)
D2 <- abs(p1.21.lm$residuals[group2] - med2)

s2bf <- (sum(D1 - mean(D1))^2 + sum(D2 - mean(D2))^2)/length(p1.21$X) - 2

sbf <- sqrt(s2bf)

tbf <- (mean(D1) - mean(D2))/(sbf*sqrt((1/sum(group1)+1/sum(group2))))

qqnorm(p1.21.lm$residuals)

qq.p1.21 <- qqnorm(p1.21.lm$residuals)

names(qq.p1.21)

cor(qq.p1.21$x, qq.p1.21$y)

plot(p1.21.lm$residuals ~ p1.21.lm$fitted.values)

bptest(p1.21.lm)

```

a. They are asymmetrical. They tend to lean towards 0.

b. There seems to be some sort of pattern 

c. Tthis shows that there's one point that is an outlier. They don't look normally distributed, but we'll check this later.  

d. There doesn't seem to be any major departures. 

e. The correlation coefficient is 0.96097 and the critical value is .879. Therefore, we conclude that the data is normally distributed. 

f. There is an obvious cone-shaped trend. This means that the the errors are not independent. 

g. the BP test statistic is 3.0628 and the p-value is 0.0801. Our level of significance is 0.10. Therefore we reject the null hypothesis that thre is constant variance. 


### 3.6 <span id=points>{5}</span><span id=report>{ / }</span>

```{r p36}
# Load the Data:
p1.22 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR22.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.22) <- c("Y","X")
```


### 3.7 <span id=points>{4}</span><span id=report>{ / }</span>

```{r p37}
# Load the Data:
p1.27 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR27.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.27) <- c("Y","X")
```


### 3.8 <span id=points>{3}</span><span id=report>{ / }</span>

```{r p38}
# Load the Data:
p1.28 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR28.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.28) <- c("Y","X")
```


### 3.13 <span id=recpoints>{3}</span><span id=report>{ 3/3 }</span>

```{r p313}
# Load the Data:
p1.20 <- read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")

# Rewrite the column names to be "Y" and "X" to match the textbook:
colnames(p1.20) <- c("Y","X")

p1.20.lm <- lm(p1.20)

yhat.p1.20 <- p1.20.lm$fitted.values

#SSPE <- 


#fstar <- (SSLF/c-2) / (SSPE/n-c)

qf(0.95,8,35)

pureErrorAnova(p1.20.lm)

```

a. $H_o$: $E{Y} = \beta_0 + \beta_1X$
  $H_a$: $E{Y} \neq \beta_0 + \beta_1X$ 

b.
If F∗ <= F conclude H0. 
If F* >= F. Conclude Ha.

F = 2.21667
F* = 0.967


Therefore, we conclude that a linear regression is appropriate for this data. 

c. I believe that a lack of fit test cannot determine constant variance or normality because constant variance is determined by any order or patterns in the time sequence plot and the lack of fit test only uses the means within the levels and the variability between the levels. There's no calculation to determine if there is constant variance within the model. The same is with normality.  

</div>










 <style>
#points {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#317eac;
}

#recpoints {
  font-size:.8em;
  padding-left:5px;
  font-weight:bold; 
  color:#7eac31;
}

#report {
  font-size:.7em;
  padding-left:15px;
  font-weight:normal; 
  color:#5a5a5a;
}

#datalink {
  font-size:.5em;
  color:#317eac;
  padding-left:5px;
}

#headnote {
  font-size:.6em;
  color:#787878;
}

#note {
  font-size:.8em;
  color:#787878;
}

#headpoints {
 font-size:12pt;
 color: #585858; 
 padding-left: 15px;
}
</style>


<footer>
</footer>



 
###Notes

F Test is 

Between Variance/Within Variance



j
 

 

 